surfing

### 2021-05-06 inst/surfing.Rmd
consistency check

The first line shows that, at one of the heats in `wct01`, `Colapinto`
came first, `Bailey` second, and `Wright` came third.  The last line
shows that, at `wct11`, `Ferreira` came first and `Medina` came
second.  We can convert this dataset into a Plackett-Luce likelihood
function but first have to remove the wildcards and also player Vries
whose maximum likelihood strength is zero.

@@

>>>>

The first line shows that, at one of the heats in `wct01`, `Colapinto`
came first, `Bailey` second, and `Wright` came third.  The last line
shows that, at `wct11`, `Ferreira` came first and `Medina` came
second.  We can convert this dataset into a Plackett-Luce likelihood
function but first have to remove the wildcards and also player
`Vries` whose maximum likelihood strength is zero.

@@

and the second step is to establish its consistency:

```{r consistencycheck,cache=TRUE}
consistency(surfing)
```
